Results

### 2018-04-16 results-simus-pres.Rmd
update figures

  results %>%
    barplot_causal() +
    geom_hline(yintercept = 0.94, linetype = 3, color = "blue") +
    facet_grid(par.dist ~ .)
}
```

@@

    results %>%
      myggplot() +
      geom_boxplot(aes_string("par.causal", y, color = "method", 
                              fill = "method"), alpha = 0.3) + 
      theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
      # facet_grid(par.model ~ par.dist) +
      labs(x = "Causal SNPs (number and location)", y = ylab, 
           fill = "Method", color = "Method") +
      theme(legend.position = "none") +
      scale_fill_manual(values = methods.color) +
      scale_color_manual(values = methods.color) +
      scale_y_continuous(limits = c(0, NA))
  }

  p1 <- results.summary %>%
    barplot_causal_one() +
    facet_grid(par.model ~ par.dist) +
    labs(y = sprintf("Mean of %d AUCs", nsimu))

@@

```{r, fig.asp = 1, out.width = "90%"}
results34 %>%
  filter(par.h2 == 0.8, par.dist == "gaussian", method %in% c("logit-simple", "PRS-max")) %>%
  myggplot() +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_boxplot(aes(method, AUC, fill = simu, color = simu), alpha = 0.3) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_grid(par.dist ~ par.causal) +
  scale_fill_brewer(type = "qual", palette = 2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  labs(x = "Method")

@@

```{r}
results35.summary %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  myggplot(aes(n.train, AUC_mean, color = method, linetype = method)) +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_line(size = 1.5) +
  geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, 
                    ymax = AUC_mean + 2 * AUC_boot), 
                size = 1.5, width = 0) +
  facet_grid(. ~ par.dist) +
  scale_x_continuous(breaks = 1:6 * 1000, minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = 0:20 / 20) +
  scale_color_manual(values = methods.color) +
  labs(x = "Size of the training set", y = "Mean of 100 AUCs", 
       color = "Method", linetype = "Method") +
  theme(legend.key.width = unit(3, "line"))

>>>>

  results %>%
    barplot_causal() +
    geom_hline(yintercept = 0.94, linetype = 3, color = "blue")
}
```

@@

    results %>%
      myggplot() +
      geom_boxplot(aes_string("par.causal", y, color = "method", 
                              fill = "method"), alpha = 0.3) + 
      theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
      labs(x = "Causal SNPs (number and location)", y = ylab, 
           fill = "Method", color = "Method") +
      theme(legend.position = "none") +
      scale_fill_manual(values = methods.color) +
      scale_color_manual(values = methods.color) +
      scale_y_continuous(limits = c(0, NA))
  }

  p1 <- results.summary %>%
    barplot_causal_one() +
    facet_grid(par.model ~ .) +
    labs(y = sprintf("Mean of %d AUCs", nsimu))

@@

```{r, fig.asp = 1, out.width = "90%"}
results34 %>%
  filter(par.h2 == 0.8, par.dist == "gaussian", method %in% c("logit-simple", "PRS-max")) %>%
  myggplot() +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_boxplot(aes(method, AUC, fill = simu, color = simu), alpha = 0.3) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_grid(. ~ par.causal) +
  scale_fill_brewer(type = "qual", palette = 2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  labs(x = "Method")

@@

```{r}
results35.summary %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  myggplot(aes(n.train, AUC_mean, color = method, linetype = method)) +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_line(size = 1.5) +
  geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, 
                    ymax = AUC_mean + 2 * AUC_boot), 
                size = 1.5, width = 0) +
  scale_x_continuous(breaks = 1:6 * 1000, minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = 0:20 / 20) +
  scale_color_manual(values = methods.color) +
  labs(x = "Size of the training set", y = "Mean of 100 AUCs", 
       color = "Method", linetype = "Method") +
  theme(legend.key.width = unit(3, "line"))
